Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
remove message comments for figures

```{r echo = FALSE}
data(closest_dist)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE}
rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 500,
                             days_include = c(-1, 0, 1))
rain_1000 <- rain_exposure %>%
        arrange(desc(tot_precip)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.factor(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
rain_1000$value <- as.numeric(rain_1000$value)
map_1000 <- county_choropleth(rain_1000,
                              title = "Hits for top 1000 Storm-County Pairs\nfor Rain > 75 mm",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

@@

```{r echo = FALSE}
distance_count <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value))
map_dist_count <- county_choropleth(distance_count, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_count + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips, value = count) %>%
              mutate(region = as.numeric(region), value = as.numeric(value))
map_counts <- county_choropleth(rain_count,
                                title = "Hits by County\nfor Rain > 75 mm",
                                legend = "Hits per County", num_colors = 9,
                                state_zoom = eastern_states)
map_counts + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

>>>>

```{r echo = FALSE, warning=FALSE, message=FALSE}
data(closest_dist)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 500,
                             days_include = c(-1, 0, 1))
rain_1000 <- rain_exposure %>%
        arrange(desc(tot_precip)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.factor(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
rain_1000$value <- as.numeric(rain_1000$value)
map_1000 <- county_choropleth(rain_1000,
                              title = "Hits for top 1000 Storm-County Pairs\nfor Rain > 75 mm",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
distance_count <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value))
map_dist_count <- county_choropleth(distance_count, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_count + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips, value = count) %>%
              mutate(region = as.numeric(region), value = as.numeric(value))
map_counts <- county_choropleth(rain_count,
                                title = "Hits by County\nfor Rain > 75 mm",
                                legend = "Hits per County", num_colors = 9,
                                state_zoom = eastern_states)
map_counts + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```
